---
title: "Interactive Client in R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interactive Client in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette shows how to build an interactive peer-to-peer chat client
in R using the PeerChat package, replicating the original client written in C.

## The C client

The original C client uses `select()` to multiplex between stdin and the
UDP socket. It supports four commands:

- `/get_user <username> <password>` — discover a peer via the server
- `/message <username> <message>` — send a message to a discovered peer
- `/ping <username>` — ping a discovered peer
- `/quit` — disconnect and exit

## R equivalent

The R script below replicates this behaviour. R does not expose
`select()` on stdin, we use can `readline()` in a loop with short non-blocking
receives between prompts.

```{r client}
library(PeerChat)

peer_chat_client <- function(username, password) {
  # Connect to the synchronization server
  peer_connect(username, password)
  cat(sprintf("Connected as '%s'. Type /help for commands.\n", username))

  repeat {
    # Non-blocking receive to process any incoming packets
    peer_receive(100L)

    # Read user input
    input <- readline("> ")
    input <- trimws(input)

    if (input == "/quit") {
      break
    } else if (input == "/help") {
      cat(
        "Commands:\n",
        "  /get_user <username> <password>  — discover a peer\n",
        "  /message  <username> <text>      — send a message\n",
        "  /ping     <username>             — ping a peer\n",
        "  /quit                            — disconnect and exit\n"
      )
    } else if (startsWith(input, "/get_user")) {
      parts <- strsplit(input, "\\s+")[[1]]
      if (length(parts) == 3) {
        peer_get_user(parts[2], parts[3])
      } else {
        cat("Usage: /get_user <username> <password>\n")
      }
    } else if (startsWith(input, "/message")) {
      parts <- strsplit(input, "\\s+", perl = TRUE)[[1]]
      if (length(parts) >= 3) {
        recipient <- parts[2]
        message <- paste(parts[-(1:2)], collapse = " ")
        tryCatch(
          peer_send_message(recipient, message),
          error = function(e) cat(sprintf("Peer '%s' not found. Use /get_user first.\n", recipient))
        )
      } else {
        cat("Usage: /message <username> <text>\n")
      }
    } else if (startsWith(input, "/ping")) {
      parts <- strsplit(input, "\\s+")[[1]]
      if (length(parts) == 2) {
        tryCatch(
          peer_send_ping(parts[2]),
          error = function(e) cat(sprintf("Peer '%s' not found. Use /get_user first.\n", parts[2]))
        )
      } else {
        cat("Usage: /ping <username>\n")
      }
    } else if (nchar(input) > 0) {
      cat("Unknown command. Type /help for usage.\n")
    }
  }

  peer_disconnect()
  cat("Disconnected.\n")
}
```

## Running the client

Start the synchronization server first on machine accessible from internet (compiled from `src/server.c`),
then launch the R client:

```{r run, eval=FALSE}
peer_chat_client("nizwan", "secret123")
```

Open a second terminal and start another client (R or C) to chat:

```{r run2, eval=FALSE}
peer_chat_client("rex", "rex_password")
```

## Example session

```
> /get_user rex rex_password
> /message rex Hello from R!
> /ping rex
> /quit
Disconnected.
```
